Appendix 4: Model Comparison Code For Manuscript

### 2025-06-19 modelcomparison_code.Rmd
fixing typo and removing exploratory analysis

```{r}
# sometimes I get strange errors about C stack which can be solved with this
data <- as.data.frame(data)
fitmodels <- TRUE # TRUE for fitting models
#fitmodels <- FALSE # TRUE for fitting models
if (!fitmodels) {
  print("Loading previously fitted models")
  load(file=here("prereg_models.rdata"))
  fit.po02ss <- models$fit.po02ss
  fit.po03ss <- models$fit.po03ss
  fit.po04ss <- models$fit.po04ss
  fit.po05ss <- models$fit.po05ss
  fit.po02 <- models$fit.po02
  fit.po03 <- models$fit.po03
  fit.po04 <- models$fit.po04
  fit.po05 <- models$fit.po05
} else{
  models <- list()
}

@@

```{r}
library(gtsummary)
library(dplyr)
library(kableExtra)

edata_clean <- data %>%
  filter(de01 == 'man' | de01 == "woman") %>%
  rename(
    Gender = de01,
    Age = de02,
    DonationEligibility = bd01,
    DonationCount = bd02,
    DonationCountLast2years = bd03,
    WeeksFromLastDonation = bd04
  )

# Create summary table
etable1 <- tbl_summary(
  data = edata_clean,
  include = c(Age, DonationEligibility, WeeksFromLastDonation, DonationCount, DonationCountLast2years),
  by = Gender,
  statistic = list(
    all_continuous() ~ "{mean} ({sd})",   # Use mean (SD) for continuous vars
    all_categorical() ~ "{n} ({p}%)"
  )
) %>%
  add_n()  # Adds total N for each group

# Output as LaTeX
as_kable_extra(etable1, format = "latex")

@@

@@

fit.po02.est %>% 
  filter(abs(est.std) < 0.3) %>% 
  select(-z,-se) %>% 
  arrange(abs(est.std)) %>% 
  # Just the loadings
  filter(op != '~1')

@@

@@

```{r}
if (fitmodels) {
  gfi<- round(
    sapply(
      list(
        SSRL=fit.po02ss,
        SSBL=fit.po03ss,
        SSRF=fit.po04ss,
        SSBL=fit.po05ss,
        LFRL=fit.po02,
        LFBL=fit.po03, 
        LFRF=fit.po04,
        LFBF=fit.po05
      ),
      function(x) fitmeasures(x,c("chisq","df","pvalue","cfi","rmsea","srmr"))
    )
    ,3)
  models[['gfi']] <- gfi
} else {
  gfi <- models$gfi
}
gfi
```

@@

```{r}
if (fitmodels) {
  save(models,file=here("prereg_models.rdata"))

>>>>

```{r}
# sometimes I get strange errors about C stack which can be solved with this
data <- as.data.frame(data)
fitmodels <- TRUE # TRUE for fitting models
#fitmodels <- FALSE # TRUE for fitting models
if (!fitmodels) {
  print("Loading previously fitted models")
  load(file=here("prereg_models.rdata"))

  fit.po02ss <- models$fit.po02ss
  fit.po03ss <- models$fit.po03ss
  fit.po04ss <- models$fit.po04ss
  fit.po05ss <- models$fit.po05ss
  fit.po02 <- models$fit.po02
  fit.po03 <- models$fit.po03
  fit.po04 <- models$fit.po04
  fit.po05 <- models$fit.po05
} else{
  models <- list()
}

@@

```{r}
#library(gtsummary)
#library(dplyr)
#library(kableExtra)

#edata_clean <- data %>%
  #filter(de01 == 'man' | de01 == "woman") %>%
  #rename(
    #Gender = de01,
    #Age = de02,
    #DonationEligibility = bd01,
    #DonationCount = bd02,
    #DonationCountLast2years = bd03,
    #WeeksFromLastDonation = bd04
  #)

# Create summary table
#etable1 <- tbl_summary(
  #data = edata_clean,
  #include = c(Age, DonationEligibility, WeeksFromLastDonation, DonationCount, DonationCountLast2years),
  #by = Gender,
  #statistic = list(
    #all_continuous() ~ "{mean} ({sd})",   # Use mean (SD) for continuous vars
    #all_categorical() ~ "{n} ({p}%)"
  #)
#) %>%
  #add_n()  # Adds total N for each group

# Output as LaTeX
#as_kable_extra(etable1, format = "latex")

@@

```
```{r}
summary(fit.po03ss, standardized=TRUE, rsquare=TRUE)
lavaan::fitmeasures(fit.po03ss,c("npar","chisq","df","cfi","rmsea","srmr"))
```

@@

fit.po02.est %>% 
  filter(abs(est.std) < 0.3) %>% 
  select(-z) %>% 
  arrange(abs(est.std)) %>% 
  # Just the loadings
  filter(op != '~1')

@@

```{r}
summary(fit.po04, standardized=TRUE, rsquare=TRUE)

@@

```{r}
if (fitmodels) {
  gfi<- round(
    sapply(
      list(
        SSRL=fit.po02ss,
        SSBL=fit.po03ss,
        SSRF=fit.po04ss,
        #typo fixed (SSBL -> SSBF)
        SSBF=fit.po05ss,
        LFRL=fit.po02,
        LFBL=fit.po03, 
        LFRF=fit.po04,
        LFBF=fit.po05
      ),
      function(x) fitmeasures(x,c("chisq","df","pvalue","cfi","rmsea","srmr"))
    )
    ,3)
  models[['gfi']] <- gfi
} else {
  gfi <- models$gfi
}
gfi
```

@@

```{r}
if (fitmodels) {
  save(models,file=here("manuscript_models.rdata"))
